---
title: "Accent_Analysis"
author: "Misaki Kato"
date: "12/12/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

Clear the environment
```{r}
rm(list = ls(all.names = TRUE))
```


```{r}
library(ggplot2)
library(dplyr)
library(lme4)
library(lsmeans)
library(lmerTest)
library(afex)
```


Read in the data
```{r}
acc.dat = read.csv("Analysis_Z.csv")
```

Look at the data & clean up data
```{r}
str(acc.dat)
acc.dat$Resp_NUM = as.numeric(as.character(acc.dat$Resp_NUM))
acc.dat$ItemNumber = as.factor(as.character(acc.dat$ItemNumber))
acc.dat$ProductionPresentationOrder = as.factor(as.character(acc.dat$ProductionPresentationOrder))
acc.dat$SentenceOrder = as.factor(as.character(acc.dat$SentenceOrder))
acc.dat$SurveyDurSec = as.numeric(as.character(acc.dat$Duration..in.seconds.))
acc.dat$ListenerID = as.factor(as.character(acc.dat$mTurkCode))
acc.dat$Talker = as.factor(as.character(acc.dat$Talker))

# rename the levels of the TalkerGroup & re-order
acc.dat$TalkerGroup = as.factor(as.character(acc.dat$TalkerGroup))
levels(acc.dat$TalkerGroup)
levels(acc.dat$TalkerGroup)[levels(acc.dat$TalkerGroup)=="NativeEnglish (NTE)"] <- "NativeEnglish"
levels(acc.dat$TalkerGroup)[levels(acc.dat$TalkerGroup)=="NativeMandarin-High (NMH)"] <- "NativeMandarin-High"
levels(acc.dat$TalkerGroup)[levels(acc.dat$TalkerGroup)=="NativeMandarin-Low (NML)"] <- "NativeMandarin-Low"
```

Plot: Raw rating
```{r}
acc.dat.plot.prep = acc.dat %>% group_by(TalkerGroup) %>% summarise(mean = mean(Resp_NUM, na.rm=TRUE), sd = sd(Resp_NUM, na.rm=TRUE), n = n(), sem=sd(Resp_NUM , na.rm=TRUE)/sqrt(n), ci=qt(0.975,df=n-1)*sem)

ggplot(data = acc.dat.plot.prep, aes(x = TalkerGroup, y = mean, ymin=mean-ci, ymax=mean+ci)) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black") + 
  geom_errorbar(width=.1, position=position_dodge(width = 0.5)) + 
  labs(y="Perceived accentedness") +
  theme(axis.title.x = element_blank(),  axis.title.y = element_text(size=18, vjust=1.5), 
        axis.text.x  = element_text(size=18, colour ="black"), axis.text.y = 
        element_text(size=20, colour ="black"), panel.background = element_rect(fill = 
        "white"), panel.grid.major = element_line(colour = "gray"), panel.grid.major.x = 
        element_blank()) + scale_y_continuous(limits = c(0,9))

## by talker
acc.dat.plot.prep2 = acc.dat %>% group_by(Talker) %>% summarise(mean = mean(Resp_NUM, na.rm=TRUE), sd = sd(Resp_NUM, na.rm=TRUE), n = n(), sem=sd(Resp_NUM, na.rm=TRUE)/sqrt(n), ci=qt(0.975,df=n-1)*sem)

ggplot(data = acc.dat.plot.prep2, aes(x = Talker, y = mean, ymin=mean-ci, ymax=mean+ci)) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black") + 
  geom_errorbar(width=.1, position=position_dodge(width = 0.5)) + 
  labs(y="Perceived accentedness") +
  theme(axis.title.x = element_blank(),  axis.title.y = element_text(size=18, vjust=1.5), 
        axis.text.x  = element_text(size=18, colour ="black"), axis.text.y = 
        element_text(size=20, colour ="black"), panel.background = element_rect(fill = 
        "white"), panel.grid.major = element_line(colour = "gray"), panel.grid.major.x = 
        element_blank()) + scale_y_continuous(limits = c(0,9))
```


Plot: Z-scored rating
```{r}
acc.dat.plotZ.prep = acc.dat %>% group_by(TalkerGroup) %>% summarise(mean = mean(zscore_Resp_NUM, na.rm=TRUE), sd = sd(zscore_Resp_NUM, na.rm=TRUE), n = n(), sem=sd(zscore_Resp_NUM, na.rm=TRUE)/sqrt(n), ci=qt(0.975,df=n-1)*sem)

ggplot(data = acc.dat.plotZ.prep, aes(x = TalkerGroup, y = mean, ymin=mean-ci, ymax=mean+ci)) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black") + 
  geom_errorbar(width=.1, position=position_dodge(width = 0.5)) + 
  labs(y="Perceived accentedness (Z-scored)") +
  theme(axis.title.x = element_blank(),  axis.title.y = element_text(size=18, vjust=1.5), 
        axis.text.x  = element_text(size=18, colour ="black"), axis.text.y = 
        element_text(size=20, colour ="black"), panel.background = element_rect(fill = 
        "white"), panel.grid.major = element_line(colour = "gray"), panel.grid.major.x = 
        element_blank()) + scale_y_continuous(limits = c(-1.5,1.5))

## by talker
acc.dat.plotZ.prep2 = acc.dat %>% group_by(Talker) %>% summarise(mean = mean(zscore_Resp_NUM, na.rm=TRUE), sd = sd(zscore_Resp_NUM, na.rm=TRUE), n = n(), sem=sd(zscore_Resp_NUM, na.rm=TRUE)/sqrt(n), ci=qt(0.975,df=n-1)*sem)

ggplot(data = acc.dat.plotZ.prep2, aes(x = Talker, y = mean, ymin=mean-ci, ymax=mean+ci)) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black") + 
  geom_errorbar(width=.1, position=position_dodge(width = 0.5)) + 
  labs(y="Perceived accentedness (Z-scored)") +
  theme(axis.title.x = element_blank(),  axis.title.y = element_text(size=18, vjust=1.5), 
        axis.text.x  = element_text(size=18, colour ="black"), axis.text.y = 
        element_text(size=20, colour ="black"), panel.background = element_rect(fill = 
        "white"), panel.grid.major = element_line(colour = "gray"), panel.grid.major.x = 
        element_blank()) + scale_y_continuous(limits = c(-1.5,1.5))
```



ANOVA - analyze the Z-scored data
```{r}
is.factor(acc.dat$TalkerGroup)
is.numeric(acc.dat$zscore_Resp_NUM)

(aov.model <- aov_car(zscore_Resp_NUM ~ TalkerGroup + Error(Talker), anova_table = list(es = "pes"), acc.dat))
```

Response: zscore_Resp_NUM
       Effect   df  MSE          F  pes p.value
1 TalkerGroup 2, 9 0.03 128.29 *** .966   <.001
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘+’ 0.1 ‘ ’ 1



# performing multiple pairwise-comparison between the means of groups.
```{r}
lsmeans(aov.model, pairwise ~ TalkerGroup, adjust="tukey") 
```

$lsmeans
 TalkerGroup          lsmean     SE df lower.CL upper.CL
 NativeEnglish       -0.9841 0.0848  9   -1.176   -0.792
 NativeMandarin-High  0.0478 0.0848  9   -0.144    0.240
 NativeMandarin-Low   0.9364 0.0848  9    0.744    1.128

Confidence level used: 0.95 

$contrasts
 contrast                                     estimate   SE df t.ratio p.value
 NativeEnglish - (NativeMandarin-High)          -1.032 0.12  9  -8.600 <.0001 
 NativeEnglish - (NativeMandarin-Low)           -1.921 0.12  9 -16.006 <.0001 
 (NativeMandarin-High) - (NativeMandarin-Low)   -0.889 0.12  9  -7.406 0.0001 

P value adjustment: tukey method for comparing a family of 3 estimates 



--- End of script ---




